Speed and Precision in Range Analysis

### 2012-05-02 doc/Manuscript/SBLP/paper.tex
Changed the author list.
Fixed English errors in SBLP paper.

\author{Victor Hugo Sperle Campos, Igor Rafael de Assis Costa,\\
Raphael Ernani Rodrigues and Fernando Magno Quint\~{a}o Pereira}

@@

\noindent
\textbf{Example.}
Continuing with our example, Figure~\ref{fig:ex_partition_grow_crop} shows
the application of our algorithm on the last strong component of
Figure~\ref{fig:overall_view}(d).
Upon meeting this SCC, we have already determined that the interval
$[0, 0]$ is bound to $i_0$ and that the interval $[100, 100]$ is bound to
$j_0$.
We are not guaranteed to find the least fix point of a constraint system.
However, in this example we did it.
We emphasize that finding this tight solution was only possible because of
the topological ordering of the constraint graph in
Figure~\ref{fig:overall_view}(d).
Had we applied the widening operator onto the whole graph, then we would
have found out that variable $j_0$ is bound to $[-\infty, +\infty]$,
because
(i) it receives its interval directly from variable $k_t$, which is upper
bounded by $+\infty$, and
(ii) it is part of a negative cycle.
On the other hand, by only analyzing $j$'s SCC after we have
analyzed $k$'s, $k$ only contribute the constant range $[0, 99]$ to $j_0$.

@@

The experiments also reveal that the memory consumption of our implementation
is linear with the program size.
Figure~\ref{fig:MemCorr} plots these two quantities together.
The linear correlation, in this case, is even stronger than that found in
Figure~\ref{fig:TimeCorr}, which compares runtime and program size: the
coefficient of determination is 0.9947.
The figure only shows our 100 largest benchmarks.
Again, SPEC \texttt{403.gcc} is the heaviest benchmark, requiring
265.588KB to run.
Memory includes stack, heap and the executable program code.

>>>>

\author{Victor Hugo Sperle Campos, Raphael Ernani Rodrigues, \\
Igor Rafael de Assis Costa and Fernando Magno Quint\~{a}o Pereira}

@@

\noindent
\textbf{Example.}
Continuing with our example, Figure~\ref{fig:ex_partition_grow_crop} shows
the application of our algorithm on the last strong component of
Figure~\ref{fig:overall_view}(d).
Upon meeting this SCC, we have already determined that the interval
$[0, 0]$ is bound to $i_0$ and that the interval $[100, 100]$ is bound to
$j_0$.
We are not guaranteed to find the least fix point of a constraint system.
However, in this example we did it.
We emphasize that finding this tight solution was only possible because of
the topological ordering of the constraint graph in
Figure~\ref{fig:overall_view}(d).
Had we applied the widening operator onto the whole graph, then we would
have found out that variable $j_0$ is bound to $[-\infty, +\infty]$,
because
(i) it receives its interval directly from variable $k_t$, which is upper
bounded by $+\infty$, and
(ii) it is part of a negative cycle.
On the other hand, by only analyzing $j$'s SCC after we have
analyzed $k$'s, $k$ only contributes the constant range $[0, 99]$ to $j_0$.

@@

The experiments also reveal that the memory consumption of our implementation
is linear with the program size.
Figure~\ref{fig:MemCorr} plots these two quantities together.
The linear correlation, in this case, is even stronger than that found in
Figure~\ref{fig:TimeCorr}, which compares runtime and program size: the
coefficient of determination is 0.9947.
The figure only shows our 100 largest benchmarks.
Again, SPEC \texttt{403.gcc} is the heaviest benchmark, requiring
265,588KB to run.
Memory includes stack, heap and the executable program code.
